Notes for General Relativity

### 2016-09-19 G.R/G.R.tex
New course note: Group theory in Physics. Modifying G.R. and green function program.

    \subsection{Light's life}
    \label{sec:Lights_life}
    The life of a proton must be miserable.

>>>>

    By similar arguments, we see that $e^{iklm}e^{npqr}$ forms a true
    tensor, so does $e^{iklm}e_{prst}$, etc.

    Also, Landau says that the only tensor that is invariant in all 
    corrdinate system is the unit tensor $\sigma^i_k$. So all the 
    above tensor should be able to be expressed in terms of this.
    The author then provides the following formulae (they are too
    complicated to type that I just paste the screenshot here):
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/{ch1.four_vectors_formulae_4_ee}.png}
        \caption{Formulae for ee}
        \label{fig:Formulae-for-ee}
    \end{figure}

    And:
    \begin{align}
        e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= -A e_{iklm} \\
        e^{iklm}e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= 24 \;\mathrm{det}(A)
    \end{align}
    Next the autho introduces the dual tensors. Since this is important
    and the case of Lorentzian spacetime is somewhat different from
    the usual case, this topic deserves a separate treatment in the
    following section.

    \subsection{Dual Tensors}
    \label{sec:Dual_Tensors}
    % TODO See this post:http://physics.stackexchange.com/questions/37577/what-does-the-dual-of-a-tensor-mean-e-g-dual-stress-tensor-in-relativistic-ed
    \subsection{Light's life}
    \label{sec:Lights_life}
    The life of a proton must be miserable.
